### 2018-06-24 source/Ch7-3C295/3c295.tex
redone figs in sec6, still need to redo them in chapter 5

\pg
A good initial test of our hypothesis that we can start from a ``good enough" point to reach a global minimum is to self-calibrate on a two-point model. We perform this test, keeping only the two brightest pixels of the model shown above to test whether we converge to the same structure. The result is shown as an overlay in \cref{fig.sc.2pt}: as we can see, we recover the same structure as the full VLA model. We therefore start from this full model for our ``proper" self-calibration procedure.
\begin{figure}[h]
\includegraphics[width=0.8\linewidth]{images/{3C_295_I_8.7GHz_lbs2003.J2000.fits2ptmodel}.png}
\caption{\label{fig.sc.2pt} Overlay of the model resulting from a self-calibration process starting from a two-point model. The overlays start at 0.9$\sigma$ of the final, 60-subband self-cal restored image, and move in increments of 6$\sigma$}.
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=0.9\linewidth]{images/{3C_295_I_8.7GHz_lbs2003.J2000.fits.overlay}.png}
\caption{\label{fig.3c295.final.overlay} Overlay of final model of 3C295 on initial VLA model. This final model is made by adding individual contributions from the spectral slices shown in \cref{fig.3c295.spectral.overlays}.}
\end{figure}
% python ~/Scripts/PngCutoutFromFits.py --filename 3C_295_I_8.7GHz_lbs2003.J2000.fits --RA 14:11:20.6 --Dec 52:12:09.0 --size .1 --invert -v --overlaymin 10 --nlevels 200 --vmin 0.06 --vmax 2 --overlay IMAGES/MSlist.fullBW.LOBOS6.MSlist.fullBW.txt.uniform.int.restored.bootstrap.fits
\pg
By inspecting individual spectral slices of our multi-spectral model in \cref{fig.3c295.spectral.overlays}, we can see that the presence of calibration artefacts is not the same at all frequencies. We see a lot of artefacts remain for the slices at 128.514 MHz, 140.428 MHz and 176.17 MHz, in particular. Note that the overlay values, calculated as a function of the noise in the image, are extremely high: this is because the source itself is extremely bright (as are, therefore, its associated calibration artefacts, which can be assimilated to the noise-PSF), with a maximum pixel value of $\sim$20 Jy, while the noise in the corner of the image is quite low, at $\sim$2mJy. In other words, because this image has a decent dynamic range (DR=10000, which is a factor of 100 lower than what is achievable with self-cal on VLA, WSRT data), the levels must be high. We note that the dynamic range here is lower than could be expected for this data if we did not use such a drastic $uv$-cut or uniform weighting, both of which ``artificially" increase the rms in the image (but are necessary to improve image deconvolution for such a diffuse source).

>>>>

\pg
A good initial test of our hypothesis that we can start from a ``good enough" point to reach a global minimum is to self-calibrate on a two-point model. We perform this test, keeping only the two brightest pixels of the model shown above to test whether we converge to the same structure. The result is shown as an overlay in \cref{fig.sc.2pt}: as we can see, we recover the same structure as the full VLA model. We therefore start from this full model for our ``proper" self-calibration procedure.
\begin{figure}[h]
\includegraphics[width=0.8\linewidth]{images/{3C_295_I_8.7GHz_lbs2003.J2000.fits2ptmodel}.png}
\caption{\label{fig.sc.2pt} Overlay of the model resulting from a self-calibration process starting from a two-point model. The overlays rise exponentially, from the $5\sigma$ level to the maximum pixel value in the image.}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=0.9\linewidth]{images/{3C_295_I_8.7GHz_lbs2003.J2000.fits.overlay}.png}
\caption{\label{fig.3c295.final.overlay} Overlay of final model of 3C295 on initial VLA model. This final model is made by adding individual contributions from the spectral slices shown in \cref{fig.3c295.spectral.overlays}.}
\end{figure}
% python ~/Scripts/PngCutoutFromFits.py --filename 3C_295_I_8.7GHz_lbs2003.J2000.fits --RA 14:11:20.6 --Dec 52:12:09.0 --size .1 --invert -v --overlaymin 10 --nlevels 200 --vmin 0.06 --vmax 2 --overlay IMAGES/MSlist.fullBW.LOBOS6.MSlist.fullBW.txt.uniform.int.restored.bootstrap.fits
\pg
By inspecting individual spectral slices of our multi-spectral model in \cref{fig.3c295.spectral.overlays}, we can see that the presence of calibration artefacts is not the same at all frequencies. We see a lot of artefacts remain for the slice at 176.17 MHz in particular, and the slice at 140.428 MHz to a lesser extent. Note that the overlay values rise exponentially. The maximum pixel value  in the image is $\sim$20 Jy, while the noise in the corner of the image is $\sim$2mJy. We achieve a relatively decent dynamic range (DR=10000, which is a factor of 100 lower than what is achievable with self-cal on VLA, WSRT data). We note that the dynamic range here is lower than could be expected for this data. This could be due, among other things, to our choices of $uv$-cut and imaging weights, both of which ``artificially" increase the rms in the image (but are necessary to improve image deconvolution for such a diffuse source.
